%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Weavering Rally Team}
    {Rally reconnaissance computer}
    {Westminster, CO} % Location
    {Nov. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Arduino based computer for preparing stage notes}
        \item {Measuring distance based on GPS and ABS wheel sensors}
        \item {Measuring corner severity using steering angle}
        \item {Developed for use by Rally.Build race shop and affiliated teams}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Weavering Rally Team}
    {Prototyping hardware for Decawave DMW1000}
    {Westminster, CO} % Location
    {Oct. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {PCB design for prototyping in KiCad}
        \item {Ranging using TOA technique on IEEE 802.15.4}
        \item {Mesh networking of embedded devices}
        \item {Developing to sell prototyping board to hobbyists}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Website for organizing and displaying rally racing scores}
    {rallyscores.com}
    {Westminster, CO} % Location
    {Jul. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Hosted on AWS EC2}
        \item {Client written using React, React Router, Express, Semantic UI, and Webpack in Javascript}
        \item {Server written using NodeJS, MongoDB, and SocketIO in Javascript}
        \item {Backend written in Python using Scrapy to gather data}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {MacOS daemon install script and testing}
    {splintermail.com}
    {Westminster, CO} % Location
    {Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Encrypted/Anonymous email service}
        \item {Local daemon and CLI written in Python}
        \item {Encryption of all email metadata on server using public key}
        \item {By-directional re-mailer for preventing websites from tracking based on email as a unique id}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fork of open source door lock smart app}
    {Automation for Airbnb using Smartthings controller}
    {Englewood, CO} % Location
    {Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {iCal parser and event logic for setting lock codes for each guest based on phone number}
        \item {Push notifications to phone app when guest uses their code for the first time}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Weavering Rally Team}
    {Co-driver computer for race car}
    {Englewood, CO} % Location
    {Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Embedded system for assisting co-driver during competition}
        \item {GPS tracking and timing on Arduino microcontroller with 7-segment display}
        \item {Competed in Rally Colorado 2017}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Automated Investment Advisor}
    {Software for identifying ideal rental properties}
    {Englewood, CO} % Location
    {Mar. 2017 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Scrapy scrapers for Realtor to find new listings}
        \item {Automated AWS EC2 Proxy instances for defeating Realtor.com tracking of bots}
        \item {MongoDb database for storing listings for analysis}
        \item {Airbnb scraper for finding similar properties listed for short term rental}
        \item {Daily PDF report generated using latex}
        \item {Developed locally and then deployed onto AWS}
        \item {Attempted to sell reports to Realtors}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Computer Vision on Embedded Hardware}
    {Colorado Robot Challenge}
    {Golden, CO} % Location
    {Oct. 2013 - Mar. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Real-time firmware for 3d stereo vision sensor on XMOS and Nvidia hardware}
        \item {Custom BCB prototyping with surface mount components}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
